%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be
                                  % changed to 11pt or 12pt here

%\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook
                      % postscript font uncomment this line and comment the one
                      % above.
%\usepackage[sfdefault]{roboto}
\usepackage{times}

\usepackage{hyperref}

\setlength{\textwidth}{5.3in} % Text width of the document

\begin{document}

%------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf David Johnston} % Your name at the top
\moveleft.5\hoffset\centerline{Software Engineer} % Your name at the top

 % Horizontal line after name; adjust line thickness by changing the '1pt'
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\moveleft.5\hoffset\centerline{\href{mailto:dwtj@iastate.edu}{dwtj@iastate.edu}}
\moveleft.5\hoffset\centerline{\url{https://github.com/dwtj}}

%------------------------------------------------------------------------------

\begin{resume}

%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelor of Engineering,} Major in Software Engineering (GPA 3.5) \\
Iowa State University, Ames, IA. (Completed December 2015)

{\sl Bachelor of Science,} Major in Mathematics + Computer Science (GPA 3.5) \\
Iowa State University, Ames, IA. (Expected May 2017)

{\sl Master of Science,} Computer Science \\
Iowa State University, Ames, IA. (Expected May 2017)


%------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%------------------------------------------------------------------------------

\section{COMPUTER \\ SKILLS}

{\sl Advanced Java:} compiler plugins (via annotation processors), reflection,
  metaprogramming, concurrency, instrumentation, program analysis (via IBM's
  WALA).

{\sl Misc:} Unix/Linux/BSD system administration; C/C++; formal verification and
  model checking (Spin); formal proof assistants (Coq); data analysis (R,
  Python, and MATLAB); Python network programming (Twisted).

%------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl ISU Graduate Research Assistant}   \hfill {\sl January 2015 -- Present} \\
  \href{http://design.cs.iastate.edu/}{ISU Laboratory for Software Design}
  \begin{itemize} \itemsep -1pt % Reduce space between items
    \item Lead dev team for @PaniniJ (\url{https://github.com/hridesh/panini}),
          a language embedded in Java for safe concurrent programming.
    \item Research techniques for novel ownership transfer check (both static
          and dynamic) for preventing certain race conditions in concurrent
          systems.
  \end{itemize}

{\sl ISU Graduate-Course Teaching Assistant}         \hfill {\sl S2013}
  \begin{itemize} \itemsep -1pt
    \item HCI 575, {\sl Computational Perception}: Created computer vision
          assignments involving MATLAB, OpenCV, and PCL; guest lectured on
          programming with OpenCV.
  \end{itemize}

{\sl ISU Undergraduate-Course Teaching Assistant}    \hfill {\sl S2012, F2013,
                                                            S2014, S2016}
  \begin{itemize} \itemsep -1pt
    \item CprE 185, {\sl Introductory C}: Co-lectured weekly recitations; guest
          lectured on pointers.
    \item CprE 281, {\sl Digital Logic}: Co-lectured weekly recitations; guest
          lectured on hardware-implemented finite state machines.
    \item ComS 319, {\sl Software Construction and User Interfaces}: Assisted
          students as they completed assignments and developed semester-long
          group projects.
    \item ComS 430, {\sl Concurrency Fundamentals and Application Integration}:
          Developed/graded students' assignments in concurrent programming
          (both thread- and actor-based); advised students with projects;
          instituted Git-based homework distribution/submission practices.
  \end{itemize}


%------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%------------------------------------------------------------------------------

\section{COMMUNITY \\ SERVICE}

  \begin{itemize}
    \item {\sl ISU SE SAC Chair:} Led ISU Software Engineering Student Advisory
          Council.
    \item {\sl ISU GPSS Senator:} Representative for CS in ISU Graduate and
          Professional Student Senate.
  \end{itemize}

%------------------------------------------------------------------------------
%	Journal Publications
%------------------------------------------------------------------------------

\section{PUBLICATIONS}

Schenck, C.; Sinapov, J.; Johnston, D.; Stoytchev, A., ``Which Object Fits Best?
Solving Matrix Completion Tasks with a Humanoid Robot," in {\sl Autonomous
Mental Development}, IEEE Transactions on , vol.6, no.3, pp.226-240, Sept. 2014

\end{resume}
\end{document}
